What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-10-26 Manuscript.qmd
Add files via upload

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - name: Thomas Reiter
    email: t.reiter@psy.lmu.de
  - name: Philipp Sterner
    email: p.sterner@psy.lmu.de
format: pdf
floatsintext: yes
editor: visual
---

@@

In a first step, potential effect heterogeneity is modeled.
Specifically, some function is estimated that relates the attribute levels of the *L* attributes that were shown to subject *i* in the $k^{th}$ round in profile *j* and the covariate vector $X_i$ to the observed binary outcome $Y_{ijk}$ (which is equal to 1 if the profile was chosen and equal to 0 if it was not chosen).
CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functionial relationship could be used as well.
BART is...

@@

# Data, Research Question, and Method
-Die Daten 
-Fragestellung 
-bisherige Forschung

# Results
-Ergebnisse 
cjBart Ergebnisse

# Integration of Results
-Einordnung der Ergebnisse
-Vergleich mit factorHet
-Vergleich mit “normaler” Subgruppen Analyse

# Discussion
Discussion & Limitations
-Tuning 
-Wie viele Covariates (inference vs. exploration)
-Stabilität

>>>>

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - name: Thomas Reiter
    email: t.reiter@psy.lmu.de
  - name: Philipp Sterner
    email: p.sterner@psy.lmu.de
format: pdf
floatsintext: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

In a first step, potential effect heterogeneity is modeled.
Specifically, some function is estimated that relates the attribute levels of the *L* attributes that were shown to subject *i* in the $k^{th}$ round in profile *j* and the covariate vector $X_i$ to the observed binary outcome $Y_{ijk}$ (which is equal to 1 if the profile was chosen and equal to 0 if it was not chosen).
CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
BART is...

@@

# Data, Research Question, and Method

-Die Daten -Fragestellung -bisherige Forschung

# Results

-Ergebnisse cjBart Ergebnisse

# Integration of Results

-Einordnung der Ergebnisse -Vergleich mit factorHet -Vergleich mit “normaler” Subgruppen Analyse

# Discussion

Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität
